The pollination trade-off

### 2018-11-21 paper/manuscript.Rmd
Insert figure question 1 in paper

```{r fig-trade-off-predictions, fig.height= 3, fig.width = 6.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen. Each dot indicates the predicted median gains for a species in its community (which correspons to the selected random effects in all of our models). The horizontal and vertical bars under each dot indicate the 0.05 bootstrap confidence intervals of the estimates. The solid lines indicate the overall relationship in each of the bootstrap replicates and were calculated by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al. 2012). The dashed line indicates the isoline at which heterospecific pollen is gained at the same rate than conspecific pollen."}
# pdf(width = 6.5, height = 3.25)
  cowplot::plot_grid(
    drake::readd(fig_con_con),
    drake::readd(fig_con_hetero_gain))
  # dev.off()
```

@@

```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates of models of conspecific (absolute and relative to the potential selfing) and heterospecific pollen density gain. Results are only shown for models that included explanatory variable. The median relative variable impotance of the four variables for each model set is shown next to each distribution. Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{S-tab:table-aic-fixed-models}) of each candidate model set that includes the variable."}
drake::readd(fig_coefficient_averages)
```

>>>>

```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen. Each dot indicates the predicted median gains for a species in its community (which correspons to the selected random effects in all of our models). The horizontal and vertical bars under each dot indicate the 0.05 bootstrap confidence intervals of the estimates. The solid lines indicate the overall relationship in each of the bootstrap replicates and were calculated by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al. 2012). The dashed line indicates the isoline at which heterospecific pollen is gained at the same rate than conspecific pollen."}

# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
# pdf(width = 6.5, height = 4)
drake::loadd(fig_random_slopes)
drake::loadd(fig_con_con)
drake::loadd(fig_hetero_con)
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
rw <- c(9,1.2, 6.5,1.2)

left <- cowplot::plot_grid(
  fig_con_con[[1]],
  fig_con_con[[2]],
  fig_hetero_con, 
  ncol = 2, 
  rel_widths = rw[c(3,4)], 
  align = "h"
)

right <- cowplot::plot_grid(
  fig_random_slopes[[1]],
  fig_random_slopes[[2]], 
  ncol = 2, 
  align = "h", 
  rel_widths = rw[1:2]
)

slopes_plot <- cowplot::plot_grid(
  right,
  left,
  ncol = 2,
  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
)
slopes_plot
# dev.off()

# pdf(width = 3.25, height = 3)
# plot_bagged_vs_open_conspecific(dep_frame)
# dev.off()

  # cowplot::plot_grid(
  #   slopes_plot, 
  #   drake::readd(fig_con_con),
  #   drake::readd(fig_con_hetero_gain), 
  #   ncol = 1, 
  #   rel_heights = c(1/2, 1/2, 1/4))

```

@@

```{r fig-model-results-global, eval = F, fig.height = 2, fig.cap = "Distribution of effect estimates of models of conspecific (absolute and relative to the potential selfing) and heterospecific pollen density gain. Results are only shown for models that included explanatory variable. The median relative variable impotance of the four variables for each model set is shown next to each distribution. Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{S-tab:table-aic-fixed-models}) of each candidate model set that includes the variable."}
drake::readd(fig_coefficient_averages)
```
